---
title: "RegressionProject"
author: "Dalton Sloan"
output: pdf_document
---

###Assignment
You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG”
"Quantify the MPG difference between automatic and manual transmissions"

###Question
Take the mtcars data set and write up an analysis to answer their question using regression models and exploratory data analyses.

Your report must be:

Written as a PDF printout of a compiled (using knitr) R markdown document.
Brief. Roughly the equivalent of 2 pages or less for the main text. Supporting figures in an appendix can be included up to 5 total pages including the 2 for the main report. The appendix can only include figures.
Include a first paragraph executive summary.
Upload your PDF by clicking the Upload button below the text box.

###Peer Grading
The criteria that your classmates will use to evaluate and grade your work are shown below. 
Each criteria is binary: (1 point = criteria met acceptably; 0 points = criteria not met acceptably)
Your Course Project score will be the sum of the points and will count as 40% of your final grade in the course. 

###Loading Data
```{r}
data(mtcars)
```

###Analysis

```{r}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
mtcars$am <- factor(mtcars$am)

summary(mtcars)
```

###Regression Model

```{r}
model <- lm(mpg ~ ., data = mtcars)
topmodel <- step(model, direction="backward")

summary(topmodel)
```

The adjusted R-squared shows roughly 85% of the variance is explained by the final model. The output of this model suggests that mpg decreases by cylinders, horsepower, and weight. Mpg increases with a manual transmission.

```{r}
par(mfrow=c(2,2))
plot(topmodel)
```

As the results show cars with a manual transmission are better for mpg than cars with an automatic transmission.
